A demonstration of the \LaTeXe\ class file for \itshape{SAGE Publications}

### 2015-12-28 body/results.tex
figures + all stats

\subsubsection{HRP-2 -- Path re-planning(Figure~\ref{fig:re-planning}):}
In this long scene, HRP-2 plans a path through through several obstacles. the scene is edited during the execution of the motion: a stair is added,
some stepping stones are removed, and part of the final staircase is deleted. All these modifications require re-planning.

@@

\begin{table*}
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{60pt} | >{\centering\arraybackslash}m{60pt} | >{\centering\arraybackslash}m{60pt} | >{\centering\arraybackslash}m{60pt} | >{\centering\arraybackslash}m{60pt} | c}
  &  Complete guide generation & Collision & Static equilibrium & ik  & Total generation time & Time per step\\
 \hline
   Steep stairs & 22 -- \textbf{33} --  76 & 1 --  \textbf{4} -- 61   & 22 --  \textbf{52} -- 534 & 108 --  \textbf{1069} -- 10550 & 267 --  \textbf{1337} -- 11484 & \textbf{66} \\
   %Standing up & $70$ & 23 & 48\\
 \end{tabular}
\caption{minimum, \textbf{average} and worst time (in ms) spent in the generation process for each scenario and each critical part of the generation process. The last
column indicates the average time necessary to compute one contact transition.}
\label{tab:requestime}
\quad
\end{table*}

@@

\subsubsection{Success rates}
Table~\ref{tab:requestpercent} summarizes the success rates obtained for each scenario.
\begin{table*}
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | c}
  &  Path planning & True feasibility & Kinematic failure & Equilibrium failure \\
 \hline
   Steep stairs & 100\%  & 99.5\% & 0.11\% & 0.39\% \\
   Standing up & 100\% & 89\% & 7\% & 4\% \\
   Truck egress & \% & \% & \% &  \% \\
   Rubble & \% & \% & \% & \% \\
   Obstacle race & \% & \% & \% & \% \\
 \end{tabular}
\caption{Success rates for each scenario. The first value indicates the percentage of successfull complete path plannings for 1000 tests; The second value
indicates the percentage of truly feasible root configurations: considering each limb individually, indicates the percentage of root placements of the guide trajectory that
led to a feasible contact. Kinematic failure is the percentage of contact generations that failed because no collision-free candidate was found. Equilibrium failure is the percentage of contact
generations that failed because no candidate respected the static equilibrium condition.}
\label{tab:requestpercent}
\quad
\end{table*}

>>>>

\subsubsection{HRP-2 -- Path re-planning(Figure~\ref{fig:re-planning}):}
In this long scene, HRP-2 plans a path through several obstacles. the scene is edited during the execution of the motion: a stair is added,
some stepping stones are removed, and part of the final staircase is deleted. All these modifications require re-planning.

@@

\begin{table*}
\centering
\small
\begin{tabular}{ l | >{\centering\arraybackslash}m{57pt} | >{\centering\arraybackslash}m{70pt} | >{\centering\arraybackslash}m{75pt} | >{\centering\arraybackslash}m{77pt} | >{\centering\arraybackslash}m{85pt} | c}
  &  Complete guide generation & Static equilibrium & Collision & ik  & Total generation time & 1 step\\
 \hline
   Stairs & 6 -- \textbf{13} --  24 & 13 --  \textbf{32} -- 329   & 1 --  \textbf{4} -- 38 & 26 --  \textbf{127} -- 1345 & 92 --  \textbf{261} -- 2174 & \textbf{14} \\
   Standing & 4 -- \textbf{451} --  985 & 27 --  \textbf{144} -- 338   & 2 --  \textbf{12} -- 37 & 144 --  \textbf{1046} -- 2374 & 310 --  \textbf{1622} -- 3429 & \textbf{66} \\
   Rubble & 3 -- \textbf{524} --  993 & 242 --  \textbf{511} -- 3480   & 233 --  \textbf{505} -- 4564 & 180 --  \textbf{414} -- 3518 & 1400 --  \textbf{3058} -- 13126 & \textbf{43} \\
   Race & 1 -- \textbf{501} --  995 & 266 --  \textbf{449} -- 3956   & 824 --  \textbf{1061} -- 2130 & 666 --  \textbf{874} -- 1613 & 2530 --  \textbf{3722} -- 10030 & \textbf{33} \\
   %Standing up & $70$ & 23 & 48\\
 \end{tabular}
\caption{minimum, \textbf{average} and worst time (in ms) spent in the generation process for each scenario and each critical part of the generation process. The last
column indicates the average time necessary to compute one contact transition.}
\label{tab:requestime}
\quad
\end{table*}

@@

\subsubsection{Success rates}
Table~\ref{tab:requestpercent} summarizes the success rates obtained for each scenario.
\begin{table*}
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | c}
  &  Path planning & True feasibility & Kinematic failure & Equilibrium failure \\
 \hline
   Steep stairs & 100\%  & 99.5\% & 0.11\% & 0.39\% \\
   Standing up & 68\% & 88\% & 6\% & 6\% \\
   %~ Truck egress & \% & \% & \% &  \% \\
   Rubble & 74\% & 97.87\% & 0.13\% & 2\% \\
   Obstacle race & 58\% & 95.7\% & 1.8\% & 2.5\% \\
 \end{tabular}
\caption{Success rates for each scenario. The first value indicates the percentage of successfull complete contact plannings for 1000 tests; The second value
indicates the percentage of truly feasible root configurations: considering each limb individually, indicates the percentage of root placements of the guide trajectory that
led to a feasible contact. Kinematic failure is the percentage of contact generations that failed because no collision-free candidate was found. Equilibrium failure is the percentage of contact
generations that failed because no candidate respected the static equilibrium condition.}
\label{tab:requestpercent}
\quad
\end{table*}
